Monte Carlo calculation to characterize neutron and gamma fields for ANITA neutron facility at TSL

### 2015-04-17 Paper2015.tex
General editing.

Fig.~\ref{fig:CUPProfile} shows neutron fluence profile at the CUP, compared with measurements.
In Fig.~\ref{fig:CUPProfile} simulated data were folded in energy with the neutron fission cross section for \U238~\cite{tbd}, replicating the measurements which were made with a \U238\ TFBC~\cite{Prokofiev2009}.
The results show\ldots
\todo{Describe the results: contours and profile at CUP}

\begin{figure}[t]
    \centering
    \includegraphics[width=\columnwidth]{CUPTOF10beamproRADECS.png}
    \caption{Neutron profile at the CUP, normalised to fluence rate on axis.}
    \label{fig:CUPProfile}
\end{figure}

@@

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{SUPNormalisedRADECS.eps}
        \subcaption{
            SUP.
            The comparison is against preliminary Geant4 modelling with a naked target model~\cite{Platt13} and against the standard facility parameterisation~\cite{Prokofiev2009}
        }
    \end{minipage}
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{ANITALetYieldnormalisedRADECS.eps}
        \subcaption{
            CUP. 
            The comparison is against the standard facility parameterisation~\cite{Prokofiev2009}
        }
    \end{minipage}
	\caption{
        Calculated neutron spectra, normalised to fluence above \SI{10}{\MeV}
    }
	\label{fig:Lethargyplots}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\columnwidth]{DiffYieldComparedSUPCUP10.eps}
    \caption{
        Differential neutron spectra at CUP and SUP, comparing results of this work to facility parameterisations~\cite{Prokofiev2009,Prokofiev14}
    }
    \label{fig:DifferentialSpectra}
\end{figure}

Neutron beam monitoring and characterisation at TSL includes time-of flight measurements with \U238\ TFBCs~\cite{Prokofiev14}.
Fig.~\ref{fig:TOFSpectra} compares simulated and measured TOF spectra at the CUP-TOF position.
The simulated CUP-TOF results were calculated for the \SI{3}{\cm} collimator, to match the measured data.
Neutron time of flight data from the simulation were folded in energy with the \U238\ fission cross-section, convolved with a \SI{5}{\ns} rectangle function approximating the primary proton micropulse shape, and overlapped at \SI{45}{\ns}, representing the timing ambiguity due to the micropulse period.
The results show\ldots
\todo{Explain what the results show.}

@@

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        \includegraphics[width=\columnwidth]{SUP10ColSpatialDistributionAllG.png}
        \subcaption{SUP}
        \label{fig:GammaSpatialDistributionSUP}
    \end{minipage}
    \begin{minipage}{\columnwidth}
        \includegraphics[width=\columnwidth]{CUP10ColSpatialDistributionAllG.png}
        \subcaption{CUP}
        \label{fig:GammaSpatialDistributionCUP}
    \end{minipage}
    \caption{Gamma spatial distribution}
    \todo{It would be better if gamma spatial distribution were expressed as dose, rather than number of photons. Not in time for the abstract submission, however!}
    \label{fig:GammaSpatialDistribution}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\columnwidth]{gDYieldcomparedRADECS.eps}
    \caption{Calculated differential gamma spectra at CUP and SUP}
    \label{fig:DifferentialGammaSpectra}
\end{figure}

@@

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{DoseVSenergySUP.eps}
        \subcaption{SUP}
        \label{fig:GammaDoseEnergySUP}
        \todo{Add gamma dose versus energy at SUP, \SI{10.2}{\cm} collimator}
    \end{minipage}
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{DoseVSenergyCUP.eps}
        \subcaption{CUP}
        \label{fig:GammaDoseEnergyCUP}
        \todo{Add gamma dose versus energy at CUP, \SI{10.2}{\cm} collimator}
    \end{minipage}
    \caption{Gamma dose spectra}
    \label{fig:GammaDoseEnergy}
\end{figure}

>>>>

Neutron beam monitoring and characterisation at TSL includes measurements with \U238\ TFBCs~\cite{Prokofiev14}.
Fig.~\ref{fig:CUPProfile} shows neutron fluence profile at the CUP, compared with measurements~\cite{Prokofiev14}.
In Fig.~\ref{fig:CUPProfile} simulated data were folded in energy with the neutron fission cross section for \U238~\cite{tbd}.
The results show\ldots
\todo{Describe the results: contours and profile at CUP}

\begin{figure}[t]
    \centering
    \includegraphics[width=\columnwidth]{CUPTOF10beamproRADECS.png}
    \caption{
        Neutron profile at the CUP, normalised to fluence rate on axis.
        \SI{10.2}{\cm} collimator}
    \label{fig:CUPProfile}
\end{figure}

Fig.~\ref{fig:TOFSpectra} compares simulated and measured TOF spectra at the CUP-TOF position.
Neutron time of flight data from the simulation were folded in energy with the \U238\ fission cross-section, convolved with a \SI{5}{\ns} rectangle function approximating the primary proton micropulse shape, and overlapped at \SI{45}{\ns}, representing the timing ambiguity due to the micropulse period.
The results show\ldots
\todo{Explain what the results show.}

@@

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{SUPNormalisedRADECS.eps}
        \subcaption{
            SUP.
            The comparison is against preliminary Geant4 modelling with a naked target model~\cite{Platt13} and against the standard facility parameterisation~\cite{Prokofiev2009}
        }
    \end{minipage}
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{ANITALetYieldnormalisedRADECS.eps}
        \subcaption{
            CUP.
            The comparison is against the standard facility parameterisation~\cite{Prokofiev2009}
        }
    \end{minipage}
	\caption{
        Calculated neutron spectra, normalised to fluence above \SI{10}{\MeV}.
        \SI{10.2}{\cm} collimator
    }
	\label{fig:Lethargyplots}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\columnwidth]{DiffYieldComparedSUPCUP10.eps}
    \caption{
        Differential neutron spectra at CUP and SUP (\SI{10.2}{\cm} collimator), comparing results of this work to facility parameterisations~\cite{Prokofiev2009,Prokofiev14}
    }
    \label{fig:DifferentialSpectra}
\end{figure}

@@

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        \includegraphics[width=\columnwidth]{SUP10ColSpatialDistributionAllG.png}
        \subcaption{Standard User Position}
        \label{fig:GammaSpatialDistributionSUP}
    \end{minipage}
    \begin{minipage}{\columnwidth}
        \includegraphics[width=\columnwidth]{CUP10ColSpatialDistributionAllG.png}
        \subcaption{Close User Position}
        \label{fig:GammaSpatialDistributionCUP}
    \end{minipage}
    \caption{
        Calculated gamma spatial distribution.
        \SI{10.2}{\cm}collimator
    }
    \todo{It would be better if gamma spatial distribution were expressed as dose, rather than number of photons. Not in time for the abstract submission, however!}
    \label{fig:GammaSpatialDistribution}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\columnwidth]{gDYieldcomparedRADECS.eps}
    \caption{
        Calculated gamma spectra at CUP and SUP.
        \SI{10.2}{\cm} collimator
    }
    \label{fig:DifferentialGammaSpectra}
\end{figure}

@@

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{DoseVSenergySUP.eps}
        \subcaption{Standard User Position}
        \label{fig:GammaDoseEnergySUP}
    \end{minipage}
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{DoseVSenergyCUP.eps}
        \subcaption{Close User Position}
        \label{fig:GammaDoseEnergyCUP}
    \end{minipage}
    \caption{
        Calculated gamma dose spectra.
        \SI{10.2}{\cm} collimator
    }
    \label{fig:GammaDoseEnergy}
\end{figure}
